DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/evaluation.tex
Minor changes to evaluation

\subsection{Setup}
The Raspberry Pi 3 Model B platform used in DeepPicar equips a Broadcom
BCM2837 SoC, which has a quad-core ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has private 32K I/D caches
and all cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV GPU, although we did
not use the GPU in our evaluation, due to the lack of sofware support
\footnote{TensorFlow currently only supports NVIDIA's GPUs.}.
For software, we use Ubuntu MATE 16.04 and TensorFlow 1.1.
We disabled DVFS (dynamic voltage frequency scaling) and
configured the clock speed of each core statically at the maximum 1.2GHz.
We use the SCHED\_FIFO real-time scheduler to schedule the CNN control
task while using the CFS when executing memory intensive co-runners.

>>>>

\subsection{Setup}
The Raspberry Pi 3 Model B platform used in DeepPicar equips a Broadcom
BCM2837 SoC, which has a quad-core ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has private 32K I/D caches
and all cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV GPU, although we do
not use the GPU in our evaluation, due to the lack of sofware support
\footnote{TensorFlow currently only supports NVIDIA's GPUs.}.
For software, we use Ubuntu MATE 16.04 and TensorFlow 1.1.
We disable DVFS (dynamic voltage frequency scaling) and
configure the clock speed of each core statically at the maximum 1.2GHz.
We use the SCHED\_FIFO real-time scheduler to schedule the CNN control
task while using the CFS when executing memory intensive co-runners.
